Borel regularity for ODEs and thimble integrals

### 2023-07-24 exp-resurgence.tex
Updates from Overleaf

The central goal of this paper is to explain, from this perspective, why Borel summation works well for the two kinds of problems exemplified in Section~\ref{intro:summation}.
\begin{enumerate}
\item Solving a linear ODE of single level~$1$ \cite[\S 2.1]{EcalleIII}\textcolor{DarkTurquoise}{\cite[Section~5.2.2.1]{diverg-resurg-iii}}. One example is Equation~\eqref{eqn:bessel-rescaled-1}. The general example is the equation $\mathcal{P} \Phi = 0$ given by a differential operator of the form
\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big], \]
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_{d-1}$ are entire functions of exponential type (i.e. $|R_j(z)|<C_j e^{a_j|z|}$ as $|z|\to+\infty$, for $C_j,a_j>0$ ).

@@

\subsubsection{Why does Borel summation work for solutions of single level-$1$ ODEs?}
As described in Section~\ref{borel-reg:explanatory-power}, we consider a linear single level-$1$ ODE $\mathcal{P}\Phi = 0$ given by a differential operator of the form
\begin{equation}\label{eqn:standard ODE}
\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big],
\end{equation}
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_d$ are entire functions of exponential type\footnote{A function $f$ is of exponential type if $|f(z)|\leq C e^{-a|z|}$ for $C,a>0$. Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]}. Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$, $P'(-\alpha_j)\neq 0$ for $j=1,...,d$ and $Q(-\alpha_j)\neq 0$. Our equation has an irregular singularity at $\infty$ \textcolor{magenta}{[Verify this more carefully! It seems like there should be $2(d-1)$ Stokes sectors, as described below]}.

@@

Classically it has been proved that the formal solutions $\series{\Psi}_j$ in \eqref{formal solution} are Borel-Laplace summable and their Borel-Laplace sums $\hat{\Psi}_j$ satisfy the original equation $\mathcal{P}\hat{\Psi}_j=0$ \cite{Ramis?}\textcolor{magenta}{[Braaksma,Loday-Richaud, check]}. Therefore, the distinguished frame of formal solutions becomes a distinguished frame of analytic solutions $\hat{\Psi}_1,...,\hat{\Psi}_d$.

@@

\begin{remark}
There are many ways to build a frame of solutions for these kinds of ODEs: formally in the $z$-plane Poincar\'e gave an explicit solution \cite{int-irreg}. Formally in the $\zeta$-plane \'Ecalle figured out how to find a frame of formal solutions of the Borel transformed ODE \textcolor{magenta}{[add reference]\cite{EcalleIII}\cite{loday-Remy2011}}. It can indeed be seen as a consequence of ``resurgence'' of the ODE. Our results show how to build a frame of solutions, analytically in the Borel plane. Furthermore, it shows we are picking the same frame: from the properties of the Laplace transform we get an analytic frame asymptotic to Poincar\'e frame $\series{\Psi}_j$. From the uniqueness result of Theorem~\ref{thm1}, we get a frame of analytic solutions equivalent to \'Ecalle's ones. 
\end{remark}

@@

Now using the steepest descendent method we can compute the asymptotic expansion of thimble integrals which in general gives a formal series $\tilde{I}_\alpha$ (see Malgrange, Pham, Andersen, Mistergad, the Stirling series for Gamma function in \cite{Maxim_slide_ERC}).

@@

We will restrict to $1$-dimensional thimble integrals, and in this special case we will define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform.  
Let $X$ be a translation surface---a Riemann surface carrying a holomorphic 1-form $\nu$. Suppose $X$ is of {\em meromorphic type}, meaning that we got it by puncturing a compact Riemann surface $\overline{X}$ at finitely many points, and $\nu$ has a pole at each puncture. A {\em translation coordinate} on $X$ is a local coordinate whose derivative is $\nu$. Take another meromorphic-type translation surface $B$ and a holomorphic map $f \maps \overline{X} \to \overline{B}$ with non--degenerate critical points \textcolor{magenta}{that sends punctures to punctures [actually, don't require this; the Orr--Sommerfeld integrals, for example, don't satisfy it]}. \textcolor{red}{Suppose every singularity of $B$ is a critical value of $f$.[Veronica: Is it a good assumption?]} \textcolor{DarkGreen}{\textbf{[Typical usage of ``Borel plane'' seems ambiguous, so maybe we can use ``Borel plane'' for $B$ and ``Borel cover'' for the Riemann surface of the Borel-transformed series. How to handle the Orr–Sommerfeld functions (\cite{dlmf}~\S 9.13)? We know $f = 4u^3 - 3u$ is the pullback of a translation coordinate, but we also need a puncture at $f(0)$\ldots]}} For each critical point $\alpha_j$, let $\Gamma_j$ be the ray going rightward from $\alpha_j$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j$ which vanishes at $\alpha_j$. These are well-defined as long as $\Gamma_j$ misses the critical values of $f$. The preimage $f^{-1}(\Gamma_j)$ is a bunch of disjoint curves \textcolor{magenta}{[add picture]}, as long as $\Gamma_j$ misses the other critical values of $f$. The Lefschetz thimble  $\Lambda_j$ can be regarded as the component of $f^{-1}(\Gamma_j)$ that goes through $\alpha_j$, oriented so that shifting it to its left would make its projection run clockwise around $\Gamma_j$. %The {\em thimble integral}
%\[ I_p = \int_{\Lambda_p} e^{-z f^*\zeta_p} \nu \]
%is a holomorphic function on the right half-plane parametrized by $z$, and it turns out to be Borel regular.

@@

\begin{theorem}[see Theorem \ref{thm:maxim}]
    Let $\tilde{I}_{j}(z)\defeq e^{-z \alpha_j}(2\pi)^{1/2} z^{-1/2} \sum_{n\geq 0}a_{j,n}z^{-n}$ be the asymptotic expansion of $I_j$ as $\Re z e^{i\theta}\to \infty$ for a generic direction $\theta$. Then:
\begin{enumerate}
\item The series $\tilde{\Phi}_j:=z^{1/2} \tilde{I}_j$ is Gevrey-1, thus $\tilde{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
\item If you continue the sum of $\tilde{\phi}_j$ along the ray going rightward from $\alpha_j$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
\item For any $\zeta$ on the ray going rightward from $\alpha_j$, we have
\begin{multline}
\hat{\phi}_{j}(\zeta)=\fracderiv{\textcolor{red}{3/2}}{\zeta}{\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\textcolor{red}{\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2} \textcolor{red}{\left( \int_{\Lambda_j(\zeta')} \nu \right)}\,d\zeta',
\end{multline}
where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j, \zeta])$. Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$. \textbf{[Be careful about the orientation of $\Lambda_j$.]}
\end{enumerate}
\end{theorem}

The idea of the proof is sketched below and represented in the following diagram:
\[
\begin{tikzcd}
{I}_{j} \arrow[rrr,"\aexp"]\arrow[dd, swap,"\laplace^{-1} "] &  & & \tilde{I}_{j}\arrow[dd,"\borel"]\\
& & &\\
\iota_j \arrow[r,equal] & \hat{\iota}_j & &\tilde{\iota}_{j} \arrow[ll, "\text{sum}"]
\end{tikzcd}
\]

On the one hand, the thimble integral $I_j$ can be regarded as a Laplace type integral, i.e. as the Laplace transform of a function $\iota_j$. In addition, $\iota_j$ can be written explicitly in an integral formula \eqref{formula1}. 
On the other hand, reading the diagram from the right-hand side, we compute the asymptotic expansion of $I_j$ using the saddle point approximation, which turns out to be a formal Gevrey-1 series. Thus, its Borel transform $\series{\iota}_j$ is a germ of holomorphic functions at $\zeta_j$ which can be summed to a holomorphic function $\hat{\iota}_j$. At this point we realise that $\iota_j$ and $\hat{\iota}_j$ are indeed the same. In a nutshell, thimble integrals are Borel regular because they are Laplace transforms.

In higher-dimensional complex manifolds, integrals over Lefschetz thimbles \textcolor{red}{[I'm not so sure]} are still Borel regular~\textbf{[``Exponential integrals, Lefschetz thimbles and linear resurgence''][``Exponential Integral'' lectures?]}. This fact plays an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities. Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \textbf{[Costin \& Kruskal, ``On optimal truncation...''],\cite{delabaere-howls}, \cite{dingle1973asymptotic}[Delabere \& Howls, Howls, Dingle]}.

@@

Furthermore, we introduce a geometric picture where the spatial domain $B$ is a translation surface. If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$. If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example. \textcolor{magenta}{[Add this part in Airy with pictures]}

@@

Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interests in mathematics and physics as a powerful alternative to Borel summability. Resurgence of lienar ODEs have been intensively studied (see Costin slides for ReNewQuantum, \cite{EcalleIII}, \cite{loday1994stokes}) and many results are also known for non linear ODEs (see \cite{schiappa-PI}, \cite{costin-PI} \textcolor{magenta}{[check also paper by Ecalle and Sauzin]}). For algebraic thimble integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see \cite{Maxim_slide_ERC}, \S 6.2 in \cite{kontsevich2022analyticity}), however for more general exponential integrals (see examples in \cite{Maxim_slide_ERC}) resurgence remains a conjecture. Despite their simplicity, our examples of linear ODEs and of 1-dimensional integrals show some features of resurgence and they are toy model to get a feeling on \'Ecalle formalism.

@@

It obeys the expected semigroup law \cite[\S 1.3]{mladenov2014advanced}
\begin{align*}
\fracderiv{\lambda}{\zeta}{\alpha}\,\fracderiv{\mu}{\zeta}{\alpha} & = \fracderiv{\lambda+\mu}{\zeta}{\alpha} & \lambda, \mu \in (-\infty, 0),
\end{align*}
and agrees with ordinary repeated integration when $\nu$ is an integer (see equation~35 in \cite{mladenov2014advanced}).

@@

\subsection{The Borel transform on Gevrey-$1$ series}
%\color{gray}
%\begin{itemize}
%\item Action on differential equations.
%\begin{itemize}
%\item No inhomogeneous terms! How is this consistent with the Laplace transform's action? Is there always an inhomogeneous solution with subexponential asymptotics?
%\end{itemize}
%\end{itemize}
%\color{black}

@@

So far, our discussion was at the level of formal series, however there is a special class of formal series that behaves well under Borel transform, meaning that their Borel transform gives a germ of holomorphic functions at the origin in $\C_{\zeta}$. These formal series are the so-called Gevrey-$1$ series:
\[\tilde{\Phi}=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-1} \rrbracket_1\]
is Gevrey-$1$ if there exists $A>0$ such that $|a_n|\leq A^n n!$ for all $n\geq 0$.\footnote{In asymptotic analysis Gevrey-$k$ series $\sum_{n\geq 0}a_nz^{-n}$ have coefficients that grow as $(n!)^{k}$, i.e. there exists $A>0$ such that $|a_n|\leq A^n (n!)^k$ for every $n\geq 0$. The Borel transform can be generalized in order to obatin germs of holomorphic function for higher Gevrey series. }

@@

\begin{lemma}
Let $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket$. Then, $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket_1$ is Gevrey-1 if and only if $\borel\textcolor{orange}{_\zeta}\tilde{\Phi}\in\C\lbrace\zeta\rbrace$ is a germ of holomorphic functions. 
\end{lemma}

In fact, we deduce that the Borel transform is an isomorphism between Gevrey-$1$ series $z^{-1}\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$. The inverse of $\borel\textcolor{orange}{_\zeta}$ is what we call a \textbf{formal Laplace transform}. In addition, in Section \ref{convolution} we will prove that the Borel transform is an algebra isomoprhisms.

@@

The space of Gevrey-$1$ formal series is a $\C$-algebra with unit $1$, thus we may wonder if $\borel$ is an algebra isomorphism between $\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$. The answer is yes, once we endow $\C\lbrace\zeta\rbrace$ with the convolution product and with the formal unit $\delta\defeq\borel_\zeta 1$. Let $\tilde{\Phi}, \tilde{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ (where we assume they are series on the fiber over $0$), then 
\[\borel_\zeta(\tilde{\Psi}\tilde{\Phi})=:\tilde{\psi}\ast\tilde{\phi}.\]

@@

the proof is a simple computation, and we refer to Definition 5.12 and Lemma 5.14 in \cite{diverg-resurg-i}.
\begin{lemma}
    Let $\alpha\in\mathbb{R}\setminus\Z_{<0}$, then $\borel_\zeta$ is an isomorphisms from Gevrey-$1$ formal power series $\C \llbracket z^{-\alpha} \rrbracket_1$ to the germs of holomorphic functions $\C \lbrace \zeta^{\alpha-1} \rbrace$, with inverse given by the formal Laplace transform.
\end{lemma}
\begin{proof}
    Let $\tilde{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-1} \rrbracket_1$ with $|a_n|\leq A^n n!$ and $A>0$ then  
\begin{align*}
\borel_\zeta (z^{-\alpha}\tilde{\Phi})&=\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}\ast\left(a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)=a_0\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}+\sum_{n\geq 0}a_{n+1}\frac{\zeta^{n+\alpha}}{\Gamma(1+n+\alpha)}
\end{align*}

@@

\begin{proof}
    If $m\neq 0$, equation \eqref{eqn:convolution} admits a unique solution. If $m=0$, then we assume $\hat{W}_m\in\R[\![\xi]\!]$ is the unique solution once we fix a normalization. Then, the formal inverse Borel transform $\tilde{W}_m\in\R^+[\![z^{-1}]\!]$ solves an algebraic equation
    \begin{equation}
        \tilde{W}(z)=\frac{m}{z}+\left[\frac{a_1}{z}+\frac{a_2}{z^2}+...+\frac{a_d}{z^d}\right]\tilde{W}(z)+c\sum_{n=0}^NR_n(z)\tilde{W}^n(z)
    \end{equation}
    where $R_n(z)$ are holomorphic in a neighborhood of infinity with $R_n(z)=O(z^{-1})$. This shows $\tilde{W}_m(z)=O(z^{-1})$ is holomorphic in $m,z$ for $m\in\C$ and $z$ in a neighbourhood of infinity (independent on $m$). Therefore, by Lemma~\ref{lemma-3.5} we deduce $\hat{W}_m$ is holomorphic in $\xi,m\in\C$ with at most exponential growth of order $1$ at infinity in $\xi$. By the general theory of ODEs, we also know $\hat{W}_m$ is real, positive and non-decreasing on $\R^+$. 
\end{proof}

@@

where $\Lambda_j$ is a thimble in $H_{z,1}^B$ through a critical point of $f$. We can distinguish between the case when $f$ has two distinct critical points $\alpha_+, \alpha_-$ and only one critical point $\alpha$. In both cases, we will compute the differential equation satisfied by $I$.

>>>>

The central goal of this paper is to explain, from this perspective, why Borel summation works well for the two kinds of problems exemplified in Section~\ref{intro:summation}.
\begin{enumerate}
\item Solving a linear ODE of single level~$1$ \cite[Section 2.1]{EcalleIII}\textcolor{DarkTurquoise}{\cite[Section~5.2.2.1]{diverg-resurg-iii}}. One example is Equation~\eqref{eqn:bessel-rescaled-1}. The general example is the equation $\mathcal{P} \Phi = 0$ given by a differential operator of the form
\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big], \]
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_{d-1}$ are entire functions of exponential type (i.e. $|R_j(z)|<C_j e^{a_j|z|}$ as $|z|\to+\infty$, for $C_j,a_j>0$ ).

@@

\subsubsection{Why does Borel summation work for solutions of single level-$1$ ODEs?}
As described in Section~\ref{borel-reg:explanatory-power}, we consider a linear single level-$1$ ODE $\mathcal{P}\Phi = 0$ given by a differential operator of the form
\begin{equation}\label{eqn:standard ODE}
\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big],
\end{equation}
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0(z^{-1}), \ldots, R_{d-1}(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$.\footnote{Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]} Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$, $P'(-\alpha_j)\neq 0$ for $j=1,...,d$ and $Q(-\alpha_j)\neq 0$. Our equation has an irregular singularity at $\infty$ \textcolor{magenta}{[Verify this more carefully! It seems like there should be $2(d-1)$ Stokes sectors, as described below]}.

@@

Classically it was proved that the formal solutions of \eqref{formal solution} are Borel-Laplace summable and their Borel-Laplace sums satisfy the original differential equation (see for example \cite{ramis1991series,malgrange92,malgrange1995sommation,diverg-resurg--ii}\textcolor{magenta}{[Braaksma,check]}). Therefore, the distinguished frame of formal solutions $\series{\Psi}_1,...,\series{\Psi}_d$ becomes a distinguished frame of analytic solutions $\hat{\Psi}_1,...,\hat{\Psi}_d$.

@@

\begin{remark}
There are many ways to build a frame of solutions for these kinds of ODEs: formally in the $z$-plane Poincar\'e gave an explicit solution \cite{int-irreg}. Formally in the $\zeta$-plane \'Ecalle figured out how to find a frame of formal solutions of the Borel transformed ODE \textcolor{magenta}{[add reference]\cite{EcalleIII,loday-Remy2011}}. It can indeed be seen as a consequence of ``resurgence'' of the ODE. Our results show how to build a frame of solutions, analytically in the Borel plane. Furthermore, it shows we are picking the same frame: from the properties of the Laplace transform we get an analytic frame asymptotic to Poincar\'e frame $\series{\Psi}_j$. From the uniqueness result of Theorem~\ref{thm1}, we get a frame of analytic solutions equivalent to \'Ecalle's ones. 
\end{remark}

@@

Now using the steepest descendent method we can compute the asymptotic expansion of thimble integrals which in general gives a formal series $\tilde{I}_\alpha$ (see Malgrange, Pham, and for more general thimble integrals see \cite[Section 1.2.2]{mistegard_phdthesis} and \cite{andersen2020resurgence}, the Stirling series for Gamma function in \cite{Maxim_slide_ERC,Maxim_talk_2023}).

@@

We will restrict to $1$-dimensional thimble integrals, and in this special case we will define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform. 
\color{DarkBlue}
Let $X$ be a translation surface---a Riemann surface carrying a holomorphic 1-form $\nu$. Suppose $X$ is of {\em meromorphic type}, meaning that we got it by puncturing a compact Riemann surface $\overline{X}$ at finitely many points, and $\nu$ has a pole at each puncture. A {\em translation coordinate} on $X$ is a local coordinate whose derivative is $\nu$. Take another meromorphic-type translation surface $B$ and a holomorphic map $f \maps \overline{X} \to \overline{B}$ with non--degenerate critical points \textcolor{magenta}{that sends punctures to punctures [actually, don't require this; the Orr--Sommerfeld integrals, for example, don't satisfy it]}. \textcolor{red}{Suppose every singularity of $B$ is a critical value of $f$.[Veronica: Is it a good assumption?]} \textcolor{DarkGreen}{\textbf{[Typical usage of ``Borel plane'' seems ambiguous, so maybe we can use ``Borel plane'' for $B$ and ``Borel cover'' for the Riemann surface of the Borel-transformed series. How to handle the Orr–Sommerfeld functions (\cite{dlmf}~\S 9.13)? We know $f = 4u^3 - 3u$ is the pullback of a translation coordinate, but we also need a puncture at $f(0)$\ldots]}} 
\color{black}
For each critical point $x_j$, let $\Gamma_j$ be the ray going rightward from the critical value $\alpha_j:=f(x_j)$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j$ which vanishes at $\alpha_j$. These are well-defined as long as $\Gamma_j$ misses the critical values of $f$. The preimage $f^{-1}(\Gamma_j)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\Gamma_j$ misses the other critical values of $f$. The Lefschetz thimble  $\Lambda_j$ can be regarded as the component of $f^{-1}(\Gamma_j)$ that goes through $x_j$, \textcolor{orange}{oriented so that shifting it to its left would make its projection run clockwise around $\Gamma_j$}.

\begin{figure}[h]
    \centering
    %\includegraphics{}
    \caption{The preimage of a ray departing from the critical value and going to infinity.}
    \label{fig:thimble_vs_rays}
\end{figure}

%The {\em thimble integral}
%\[ I_p = \int_{\Lambda_p} e^{-z f^*\zeta_p} \nu \]
%is a holomorphic function on the right half-plane parametrized by $z$, and it turns out to be Borel regular.

@@

\begin{theorem}[see Theorem \ref{thm:maxim}]
    Let $\tilde{I}_{j}(z)\defeq e^{-z \alpha_j}(2\pi)^{1/2} z^{-1/2} \sum_{n\geq 0}a_{j,n}z^{-n}$ be the asymptotic expansion of $I_j$ as $\Re z e^{i\theta}\to \infty$ for a generic direction $\theta$. Then:
\begin{enumerate}
\item The series $\tilde{\Phi}_j:=z^{1/2} \tilde{I}_j$ is $1$-Gevrey, thus $\tilde{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
\item If you continue the sum of $\tilde{\phi}_j$ along the ray going rightward from $\alpha_j$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
\item For any $\zeta$ on the ray going rightward from $\alpha_j$, we have
\begin{multline}
\hat{\phi}_{j}(\zeta)=\fracderiv{\textcolor{red}{3/2}}{\zeta}{\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\textcolor{red}{\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2} \textcolor{red}{\left( \int_{\Lambda_j(\zeta')} \nu \right)}\,d\zeta',
\end{multline}
where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j, \zeta])$. Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$. \textbf{[Be careful about the orientation of $\Lambda_j$.]}
\end{enumerate}
\end{theorem}

The idea of the proof is sketched below in the following diagram:
\[
\begin{tikzcd}
{I}_{j} \arrow[rrr,"\aexp"]\arrow[dd, swap,"\laplace^{-1} "] &  & & \tilde{I}_{j}\arrow[dd,"\borel"]\\
& & &\\
\iota_j \arrow[r,equal] & \hat{\iota}_j & &\tilde{\iota}_{j} \arrow[ll, "\text{sum}"]
\end{tikzcd}
\]

on the one hand, the thimble integral $I_j$ can be regarded as a Laplace type integral, i.e. as the Laplace transform of a function $\iota_j$. In addition, $\iota_j$ can be written explicitly in an integral formula \eqref{formula1}. 
On the other hand, reading the diagram from the right-hand side, we compute the asymptotic expansion of $I_j$ using the saddle point approximation, which turns out to be a formal $1$-Gevrey series. Thus, its Borel transform $\series{\iota}_j$ is a germ of holomorphic functions at $\alpha_j$ which can be summed to a holomorphic function $\hat{\iota}_j$. At this point, we realize that $\iota_j$ and $\hat{\iota}_j$ are indeed the same. In a nutshell, thimble integrals are Borel regular because they can be turned into Laplace transforms.

In higher-dimensional complex manifolds, integrals over Lefschetz thimbles \textcolor{red}{[I'm not so sure]} are still Borel regular~\textbf{[``Exponential integrals, Lefschetz thimbles and linear resurgence''][``Exponential Integral'' lectures?]}. This fact plays an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities. Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \textbf{[Costin \& Kruskal, ``On optimal truncation...''],\cite{delabaere-howls,dingle1973asymptotic}[Delabere \& Howls, Howls, Dingle]}.

@@

Furthermore, we introduce a geometric picture where the spatial domain $B$ is a translation surface. If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$. If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example (see Figure \ref{fig:different_fibres}).

\begin{figure}[h]
    \centering
    %\includegraphics[]{}
    \caption{The fiber over an ordinary point of the translation surface $B$ is a copy of the complex plane. However, the fiber over a singular point of $B$ has an interesting structure. Here we represent the example of Airy functions.}
    \label{fig:different_fibres}
\end{figure}

@@

Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interests in mathematics and physics as a powerful alternative to Borel summability. Resurgence of lienar ODEs have been intensively studied (see Costin slides for ReNewQuantum, \cite{EcalleIII,loday1994stokes}) and many results are also known for non linear ODEs (see \cite{schiappa-PI}, \cite{costin-PI} \textcolor{magenta}{[check also paper by Ecalle and Sauzin]}). For algebraic thimble integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see \cite{Maxim_slide_ERC}, \S 6.2 in \cite{kontsevich2022analyticity}), however for more general exponential integrals (see examples in \cite{Maxim_slide_ERC}) resurgence remains a conjecture. Despite their simplicity, our examples of linear ODEs and of 1-dimensional integrals show some features of resurgence and they are toy model to get a feeling on \'Ecalle formalism.

@@

It obeys the expected semigroup law \cite[Section  1.3]{mladenov2014advanced}
\begin{align*}
\fracderiv{\lambda}{\zeta}{\alpha}\,\fracderiv{\mu}{\zeta}{\alpha} & = \fracderiv{\lambda+\mu}{\zeta}{\alpha} & \lambda, \mu \in (-\infty, 0),
\end{align*}
and agrees with ordinary repeated integration when $\nu$ is an integer (see equation~35 in \cite{mladenov2014advanced}).

@@

\subsection{The Borel transform on $1$-Gevrey series}
%\color{gray}
%\begin{itemize}
%\item Action on differential equations.
%\begin{itemize}
%\item No inhomogeneous terms! How is this consistent with the Laplace transform's action? Is there always an inhomogeneous solution with subexponential asymptotics?
%\end{itemize}
%\end{itemize}
%\color{black}

@@

So far, our discussion was at the level of formal series, however there is a special class of formal series that behaves well under Borel transform, meaning that their Borel transform gives a germ of holomorphic functions at the origin in $\C_{\zeta}$. These formal series are the so-called $1$-Gevrey series:
\[\tilde{\Phi}=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-1} \rrbracket_1\]
is $1$-Gevrey if there exists $A>0$ such that $|a_n|\leq A^n n!$ \textcolor{magenta}{[isn't it $\lesssim$\,?]} for all $n\geq 0$.\footnote{In asymptotic analysis $k$-Gevrey series $\sum_{n\geq 0}a_nz^{-n}$ have coefficients that grow as $(n!)^{k}$, i.e. there exists $A>0$ such that $|a_n|\leq A^n (n!)^k$ for every $n\geq 0$. The Borel transform can be generalized in order to obatin germs of holomorphic function for higher Gevrey series. }

@@

\begin{lemma}
Let $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket$. Then, $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket_1$ is $1$-Gevrey if and only if $\borel\textcolor{orange}{_\zeta}\tilde{\Phi}\in\C\lbrace\zeta\rbrace$ is a germ of holomorphic functions. 
\end{lemma}

In fact, we deduce that the Borel transform is an isomorphism between $1$-Gevrey series $z^{-1}\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$. The inverse of $\borel\textcolor{orange}{_\zeta}$ is what we call a \textbf{formal Laplace transform}. In addition, in Section \ref{convolution} we will prove that the Borel transform is an algebra isomoprhisms.

@@

The space of $1$-Gevrey formal series is a $\C$-algebra with unit $1$, thus we may wonder if $\borel$ is an algebra isomorphism between $\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$. The answer is yes, once we endow $\C\lbrace\zeta\rbrace$ with the convolution product and with the formal unit $\delta\defeq\borel_\zeta 1$. Let $\tilde{\Phi}, \tilde{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ (where we assume they are series on the fiber over $0$), then 
\[\borel_\zeta(\tilde{\Psi}\tilde{\Phi})=:\tilde{\psi}\ast\tilde{\phi}.\]

@@

the proof is a simple computation, and we refer to Definition 5.12 and Lemma 5.14 in \cite{diverg-resurg-i}.
\begin{lemma}
    Let $\alpha\in\mathbb{R}\setminus\Z_{<0}$, then $\borel_\zeta$ is an isomorphisms from $1$-Gevrey formal power series $\C \llbracket z^{-\alpha} \rrbracket_1$ to the germs of holomorphic functions $\C \lbrace \zeta^{\alpha-1} \rbrace$, with inverse given by the formal Laplace transform.
\end{lemma}
\begin{proof}
    Let $\tilde{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-1} \rrbracket_1$ with $|a_n|\leq A^n n!$ and $A>0$ then  
\begin{align*}
\borel_\zeta (z^{-\alpha}\tilde{\Phi})&=\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}\ast\left(a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)=a_0\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}+\sum_{n\geq 0}a_{n+1}\frac{\zeta^{n+\alpha}}{\Gamma(1+n+\alpha)}
\end{align*}

@@

\begin{proof}
    If $m\neq 0$, equation \eqref{eqn:convolution} admits a unique solution. If $m=0$, then we assume $\hat{W}_m\in\R[\![\xi]\!]$ is the unique solution once we fix a normalization. Then, the formal inverse Borel transform $\tilde{W}_m\in\R^+[\![z^{-1}]\!]$ solves an algebraic equation
    \begin{equation}
        \tilde{W}(z)=\frac{m}{z}+\left[\frac{a_1}{z}+\frac{a_2}{z^2}+...+\frac{a_d}{z^d}\right]\tilde{W}(z)+c\sum_{n=0}^NR_n(z)\tilde{W}^n(z)
    \end{equation}
    where $R_n(z)$ \textcolor{orange}{[maybe write these as $R_n(z^{-1})$ to match statement of ODE result]} are holomorphic in a neighborhood of infinity with $R_n(z)=O(z^{-1})$. This shows $\tilde{W}_m(z)=O(z^{-1})$ is holomorphic in $m,z$ for $m\in\C$ and $z$ in a neighbourhood of infinity (independent on $m$). Therefore, by Lemma~\ref{lemma-3.5} we deduce $\hat{W}_m$ is holomorphic in $\xi,m\in\C$ with at most exponential growth of order $1$ at infinity in $\xi$. By the general theory of ODEs, we also know $\hat{W}_m$ is real, positive and non-decreasing on $\R^+$. 
\end{proof}

@@

where $\Lambda_j$ is a thimble in $H_{1}^{B,z}$ through a critical point of $f$. We can distinguish between the case when $f$ has two distinct critical points $x_+, x_-$ and only one critical point $x$. In both cases, we will compute the differential equation satisfied by $I$.
